% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Wenxuan Wu}

\basicInfo{
  \email{wwx0306@foxmail.com} \textperiodcentered\ 
  \phone{(+86) 19115946187} \textperiodcentered\ 
  \linkedin[Wenxuan Wu]{https://www.linkedin.com/in/wenxuan-wu-5704b88b}}

\section{\faUsers\ Work experience}
\datedsubsection{\textbf{ThunderSoft Inc.} Chengdu, China}{Sep.2024 -- Present}
\role{Java, Android, WiFi, wireshark, qnx} {Senior Network engineer}
Mainly focus on gm WiFi driver and WiFi Android framework related issues.
\begin{itemize}
\item Android WiFi feature and bug analysis.
\item WiFi driver related network issues protocol, feature, procedure (auth, handshake, etc).
\item Performance issuse focus on WiFi driver, netstack(qnx<->android), GM Android WiFi related framework.
\end{itemize}

\datedsubsection{\textbf{TD-tech.Co.} Chengdu, China}{Jul.2023 -- Sep.2024}
\role{C, git, gdb, linux, shell, vscode} {Senior network engineer}
Mainly engaged in the adaptation of 5G modules to different hardware platforms
\begin{itemize}
\item fix netstack related performance issues.
\item Adaptation of 5G modules and switching chips.
\end{itemize}

\datedsubsection{\textbf{Seanet of Chinese academy of science Co.} Chengdu, China}{Sep.2022 -- Jul.2023}
\role{C, git, gdb, linux, shell, vscode} {Senior network engineer}
Implement seanet related feature(network protocol stack,  seanet capability analizing tool)
\begin{itemize}
\item Design and implement seanet high reliable protocol and feature.
\item Design and implement seanet pkt reorder module.
\item Seanet current modules bug fix and maintainence.
\item seanet network analizer, evaluate our transport layer protocol capbilities like multipath, stealth, high reliable etc.
\item As maintainer, review project related commits and fix, design discuss and perf impovement.
\item Support test team to change and define testcase accordingly.
\end{itemize}

\datedsubsection{\textbf{ThunderSoft Inc.} Chengdu, China}{Nov.2021 -- Jul.2022}
\role{C, git, gdb, linux, shell, vscode}{Intel driver engineer}
Intel high performance network card driver(ixgbe, igb, ice etc.) feature implementation and maintainence.
\begin{itemize}
\item Implemented header split feature which is based on protocol (udp, l2, l3, inner/outer mac, sctp) regardless of tunnel.
\item Bug fix, root cause analysis, solution discussision, implementation, patch work. 
\item Code review, design discussion, solution discussion.
\item Support test team to change test case accordingly.
\end{itemize}

\datedsubsection{\textbf{Baicells Inc.} Chengdu, China}{Apr.2019 -- Nov.2021}
\role{C, git, gdb, linux, shell, vscode}{Driver engineer}
Multipath TCP which can take the full bandwidth of our CPE device  is introduced in our new released CPE device.
\begin{itemize}
\item Implemented mptcp client config module, userspace app to read and write config to kernel module through ioctl(kernel and userspace interaction).
\item Design discussion, bug fix, feature implementation. lib design related discussions. 
\end{itemize}

\datedsubsection{\textbf{State Grid.} Inner mongolia, China}{Jan. 2013 -- Oct.2018}
\role{Network, shell, router switch related configuration, Linux}{Maintainer}
Main responsibility, network maintainence of more than 200 related transformer substations.
In charge of network maintainence, fiber and network devices, network planning, network problems analysis.
\begin{itemize}
\item Maintainer of network related devices(switches, router, firewall) etc.
\item Network design and plan (ip route, config, plan).
\item Network problem analysis.
\item Netework Solution analysis.
\end{itemize}


% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Sichuan University}, Chengdu, China}{2010 -- 2013}
\textit{M.S.} in Software Engineering 
\datedsubsection{\textbf{Sichuan University}, Chengdu, China}{2006 -- 2010}
\textit{B.S.} in Software Engineering 

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C == shell > C++  > Python > Java
  \item Platform: Linux
  \item Development: driver, kernel, network stack.
\end{itemize}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/wuwenxux
  \item Languages: English - Fluent, Mandarin - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
